Enhanced Material Point Method to face dynamic problems: Local-maximum entropy approximation and explicit predictor-corrector scheme\\ \PNA{On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}

### 2020-04-27 LME-MPM.tex
Nuevo pdf (merge)

application of this capability, in this publication authors smooth 
oscillations due to excess of pore water pressure in consolidation
problems.}A proof of this statements is observed in figure~\ref{fig:LME_MPM}.

@@

\section{Conclusions}
\label{sec:conclusions}
We have developed a novel time integration scheme for \acrshort{mpm}, and
proved how local \textit{max-ent} approximation scheme could be
employed as an useful technique in \acrshort{mpm}. The \acrshort{npc} arise as a highly
efficient alternative for challenging dynamic problems like coupled
$u-p_w$ without appeal to expensive implicit time integration
algorithms. Also the procedure employed to design the \acrshort{npc} algorithm open
the door to revisit a huge variety of time integration schemes
developed originally for \acrshort{fem}, which can be rearranged to \acrshort{mpm} framework
with some modifications. Anyway, further research should be done to improve the
formal comprehension of the algorithm good performance. This paper
also enhances the suitability of the \acrshort{lme} approximation as a
general promising alternative to the wide range of approximation.
techniques developed for the \acrshort{mpm} to overcome grid crossing
limitations and to avoid the constriction of the \acrshort{ugimp} of a regular mesh
or a high density of particles per cell. Future research of the
group will be on the employ of this scheme to improve the localization
capabilities of \acrshort{mpm} for viscoplastic materials. Finally we remark on
the possibility of adapting the function $\beta(\vect{x})$ as a second
order tensor with the aim of adapt the shape function with the strain field which improves the
performance of it in the aforementioned localization
capabilities. Other possibility is to adapt the value of $\beta$ to
solve the equations \acrshort{fem}-like of meshfree-like depending of how behaves
the region, this could be extremely useful in simulating all together
initialization and propagation of fast landslides.

\begin{acknowledgements}
If you'd like to thank anyone, place your comments here
and remove the percent signs.
\end{acknowledgements}

% 
\section*{Conflict of interest}
%
The authors declare that they have no conflict of interest.

>>>>

application of this capability, where publication oscillations due to
excess of pore water pressure in consolidation problems are smoothed out by using this technique.}A proof of this statements is observed in figure~\ref{fig:LME_MPM}.

@@

\section{Conclusions}
\label{sec:conclusions}
We have developed a novel time integration scheme for
\acrshort{mpm}. The \acrshort{npc} arise as a highly efficient
alternative for demanding dynamic problems like coupled $u-p_w$
without appeal to expensive implicit time integration algorithms. Also
the procedure employed to design the \acrshort{npc} algorithm open the
door to revisit a huge variety of time integration schemes developed
originally for \acrshort{fem}, which can be rearranged to
\acrshort{mpm} framework with some modifications. Anyway, further
research should be done to elucidate the formal comprehension of the
algorithm good performance. This paper also enhances the skills of
local \textit{max-ent} approximation scheme as a robust and versatile
tool in the \acrshort{mpm} framework. It also come up as a promising
alternative to other approximation techniques developed for the
\acrshort{mpm} to overcome grid crossing limitations and to avoid the
constriction of the \acrshort{ugimp} of a regular mesh or a high
density of particles per cell. Future research of the group will be on
the employ of this scheme to strengthen the localization capabilities of
\acrshort{mpm} for viscoplastic materials. Finally we remark on the
possibility of adapting the function $\beta(\vect{x})$ through the finite strain
tensor in order to guide the shape function in the principal strain
direction to way select the most suitable set of nodes. Other
research line is the possibility to adapt the value of $\beta$ to solve the equations
\acrshort{fem}-like of meshfree-like depending of how behaves the
region, this could be extremely useful to reproduce such challenging
scenarios as simulating simultaneously both initialization and
propagation stages of fast landslides.
% 
\section*{Conflict of interest}
%
The authors declare that they have no conflict of interest.
